Evaluating FAIR Digital Object as a distributed object system

### 2023-02-02 latex/main.tex
updated FDO specs now mostly published

The FAIR Digital Object Forum \autocite{FAIRDigitalObjects} working groups are preparing more detailed \href{https://docs.google.com/spreadsheets/d/1O1PTLmVWqjQgvJsIcPgaZJe9BntHZt8_QndEG0eRwUY/edit}{requirement documents} setting out the path for realising FDOs, named \emph{FDO Recommendations}. As of 2023-01-05, these documents are in draft stages in Google Docs for internal review and have not yet formally been made public. As these drafts clarify the future aims and focus of FAIR Digital Objects, we provide their brief summaries below:

>>>>

The FAIR Digital Object Forum \autocite{FAIRDigitalObjects} working groups have prepared detailed requirement documents \autocite{fdo-specs} setting out the path for realising FDOs, named \emph{FDO Recommendations}. As of 2023-02-02, most of these documents are open for public review, while some are still in draft stages in Google Docs for internal review. As these documents clarify the future aims and focus of FAIR Digital Objects, we provide their brief summaries below:
